---
title: "Untitled"
author: "Yongzhe Wang"
output: pdf_document
---

- Packages 
```{r}
options(java.parameters = "-Xmx8g")
#install.packages("lattice")
#install.packages("nnet")
#install.packages("mice")
#install.packages("mi")
#install.packages("Amelia")
#install.packages("car")
#install.packages("corrplot")
#install.packages("boot")
#install.packages("OutlierDetection") 
#install.packages("extraTrees")
#install.packages("caret")
#install.packages("neuralnet")
#install.packages("randomForest")
#install.packages("gbm")
#install.packages("leaps")
#install.packages("glmnet")
#install.packages("doParallel")
#install.packages("foreach")
#install.packages("pROC")
#install.packages("xgboost")
library(xgboost)
library(glmnet)
library(doParallel)
library(foreach)
library(pROC)
library(gbm)
library(randomForest)
library(neuralnet)
#library(OutlierDetection)
library(lattice)
library(MASS)
library(nnet)
library(mice)
library(mi)
library(car)
library(corrplot)
library(boot)
library(caret)
library(extraTrees)
library(leaps)
library(kernlab)
library(nnet)
library(rJava)
#load("RData")
```

- Read result.data.3
```{r}
result.data.3 <- read.csv("result_data_3.csv")
result.data.3 <- result.data.3[,-1]
result.data.3
```

- Linear model for 3 days (refine)
```{r}
summary(p1  <- powerTransform(X3d.strength..psi. ~ FIneness..m2.kg. + SO3.... + CaO.... + Al2O3.... + SiO2.... + K2O_pct + C2S_pct, data = result.data.2))
lmmodel_3 <- lm(X3d.strength..psi.^1.29 ~ FIneness..m2.kg. + SO3.... + CaO.... + Al2O3.... + SiO2.... + K2O_pct + Fe2O3...., data = result.data.2)
summary(lmmodel_3)
plot(lmmodel_3)

```

- KNN model for 3 days (refine)
```{r}
set.seed(3)
ctrl <- trainControl(method = "cv", number = 5)
train(x = result.data.2[,c(1:5,8,14)], y = result.data.2$X3d.strength..psi., method = "knn" , metric = "RMSE", trControl = ctrl)$bestTune$k
KNN <- knnreg(x = result.data.2[,c(1:5,8,14)], y = result.data.2$X3d.strength..psi., k = 7)
KNN.pred<-predict(KNN,result.data.2[,c(1:5,8,14)])
SSE <- sum( (result.data.2$X3d.strength..psi. - KNN.pred)^2 )
SST <- sum( (result.data.2$X3d.strength..psi. - mean(result.data.2$X3d.strength..psi.))^2 )
R_sq <- 1 - SSE/SST
R_sq
```

- Bagged for 3 days (refine)
```{r}
control <- trainControl(method = "cv",number = 5,search = "grid")
set.seed(3)
tunegrid <- expand.grid(mtry = 7)
bagged_train <- train(X3d.strength..psi. ~ FIneness..m2.kg. + SO3.... + CaO.... + Al2O3.... + SiO2.... + K2O_pct + C2S_pct,data = result.data.2,methods = "rf",metric = "RMSE",tuneGrid = tunegrid, trControl = control)
print(bagged_train)
bagged_train$results$Rsquared
```

- Random forests for 3 days (refine)
```{r}
control_rf <- trainControl(method = "repeatedcv",number = 5,repeats = 3,search = "grid")
set.seed(3)
tunegrid_rf <- expand.grid(mtry = c(2:7))
rf_train <- train(X3d.strength..psi. ~ FIneness..m2.kg. + SO3.... + CaO.... + Al2O3.... + SiO2.... + K2O_pct + C2S_pct,data = result.data.2,methods = "rf",metric = "RMSE",tuneGrid = tunegrid_rf, trControl = control_rf)
print(rf_train)
```

- Boosting for 3 days (refine)
```{r}
set.seed(5)
control_boosting <- trainControl(method = "repeatedcv",number = 5,repeats = 10)
boosting_train <- train(X3d.strength..psi. ~ FIneness..m2.kg. + SO3.... + CaO.... + Al2O3.... + SiO2.... + K2O_pct + C2S_pct,data = result.data.2,method = "gbm", verbose = F, trControl = control_boosting)
boosting_train$bestTune

```

- Extremely random forests for 3 days (refine)
```{r}
et_grid <- expand.grid(mtry = 2:7,numRandomCuts = 1:5)
set.seed(3)
control_et = trainControl(method = "cv", number = 5)
et_train <- train(X3d.strength..psi. ~ FIneness..m2.kg. + SO3.... + CaO.... + Al2O3.... + SiO2.... + K2O_pct + C2S_pct,data = result.data.2,method = "extraTrees",numThreads = 4, tuneGrid = et_grid,trControl = control_et)
et_train
```

- Linear model for 7 days (refine)
```{r}
summary(p7 <- powerTransform(X7d.strength..psi. ~ FIneness..m2.kg. + SO3.... + CaO.... + Al2O3.... + SiO2.... + Fe2O3.... + C3S_pct + C2S_pct, data = result.data.3))
lmmodel_7 <- lm(X7d.strength..psi.^1.61 ~ FIneness..m2.kg. + SO3.... + CaO.... + Al2O3.... + SiO2.... + Fe2O3.... + C3S_pct + C2S_pct, data = result.data.3)
summary(lmmodel_7)
plot(lmmodel_7)
```

- KNN for 7 days (refine)
```{r}
set.seed(3)
ctrl <- trainControl(method = "cv", number = 5)
train(x = result.data.2[,c(1:8)], y = result.data.2$X7d.strength..psi., method = "knn" , metric = "RMSE", trControl = ctrl)
KNN <- knnreg(x = result.data.2[,1:8], y = result.data.2$X7d.strength..psi., k = 9)
KNN.pred<-predict(KNN,result.data.2[,1:8])
SSE <- sum( (result.data.2$X7d.strength..psi. - KNN.pred)^2 )
SST <- sum( (result.data.2$X7d.strength..psi. - mean(result.data.2$X7d.strength..psi.))^2 )
R_sq <- 1 - SSE/SST
R_sq
```

- Bagged for 7 days (refine)
```{r}
control <- trainControl(method = "cv",number = 5,search = "grid")
set.seed(3)
tunegrid <- expand.grid(mtry = 8)
bagged_train <- train(X7d.strength..psi. ~ FIneness..m2.kg. + SO3.... + CaO.... + Al2O3.... + SiO2.... + Fe2O3.... + C3S_pct + C2S_pct,data = result.data.2,methods = "rf",metric = "RMSE",tuneGrid = tunegrid, trControl = control)
print(bagged_train)
```

- Boosting for 7 days (refine)
```{r}
set.seed(3)
control_boosting <- trainControl(method = "repeatedcv",number = 5,repeats = 10)
boosting_train <- train(X7d.strength..psi. ~ FIneness..m2.kg. + SO3.... + CaO.... + Al2O3.... + SiO2.... + Fe2O3.... + C3S_pct + C2S_pct,data = result.data.2,method = "gbm", verbose = F, trControl = control_boosting)
boosting_train
```

- Random forests for 7 days (refine)
```{r}
control_rf <- trainControl(method = "repeatedcv",number = 5,repeats = 3,search = "grid")
set.seed(3)
tunegrid_rf <- expand.grid(mtry = c(2:8))
rf_train <- train(X7d.strength..psi. ~ FIneness..m2.kg. + SO3.... + CaO.... + Al2O3.... + SiO2.... + Fe2O3.... + C3S_pct + C2S_pct,data = result.data.2,methods = "rf",metric = "RMSE",tuneGrid = tunegrid_rf, trControl = control_rf)
print(rf_train)
```

- Extremely random forests for 7 days (refine)
```{r}
et_grid <- expand.grid(mtry = 2:8,numRandomCuts = 1:5)
set.seed(3)
control_et = trainControl(method = "cv", number = 5)
et_train <- train(X7d.strength..psi. ~ FIneness..m2.kg. + SO3.... + CaO.... + Al2O3.... + SiO2.... + Fe2O3.... + C3S_pct + C2S_pct,data = result.data.2,method = "extraTrees",numThreads = 4, tuneGrid = et_grid,trControl = control_et)
et_train
```

- Linear model for 28 days (refine)
```{r}
summary(p28 <- powerTransform(X28d.strength..psi. ~  FIneness..m2.kg. + SO3.... + CaO.... + Al2O3.... + C3A_pct + C2S_pct + Na2O_pct + K2O_pct, data = result.data.3))
lmmodel_28 <- lm(X28d.strength..psi.^1.54 ~ FIneness..m2.kg. + SO3.... + CaO.... + Al2O3.... + C3A_pct + C2S_pct + Na2O_pct + K2O_pct, data = result.data.3)
summary(lmmodel_28)
plot(lmmodel_28)
vif(lmmodel_28)
```

- KNN for 28 days (refine)
```{r}
set.seed(3)
ctrl <- trainControl(method = "cv", number = 5)
train(x = result.data.2[,c(1:4,8,9,13,14)], y = result.data.2$X28d.strength..psi., method = "knn" , metric = "RMSE", trControl = ctrl)
KNN <- knnreg(x = result.data.2[,c(1:4,8,9,13,14)], y = result.data.2$X28d.strength..psi., k = 9)
KNN.pred<-predict(KNN,result.data.2[,c(1:4,8,9,13,14)])
SSE <- sum( (result.data.2$X28d.strength..psi. - KNN.pred)^2 )
SST <- sum( (result.data.2$X28d.strength..psi. - mean(result.data.2$X28d.strength..psi.))^2 )
R_sq <- 1 - SSE/SST
R_sq
```

- Bagged for 28 days (refine)
```{r}
control <- trainControl(method = "cv",number = 5,search = "grid")
set.seed(3)
tunegrid <- expand.grid(mtry = 8)
bagged_train <- train(X28d.strength..psi. ~ FIneness..m2.kg. + SO3.... + CaO.... + Al2O3.... + C3A_pct + C2S_pct + Na2O_pct + K2O_pct,data = result.data.2,methods = "rf",metric = "RMSE",tuneGrid = tunegrid, trControl = control)
print(bagged_train)
```

- Boosting for 28 days (refine)
```{r}
set.seed(3)
control_boosting <- trainControl(method = "repeatedcv",number = 5,repeats = 10)
boosting_train <- train(X28d.strength..psi. ~ FIneness..m2.kg. + SO3.... + CaO.... + Al2O3.... + C3A_pct + C2S_pct + Na2O_pct + K2O_pct,data = result.data.2,method = "gbm", verbose = F, trControl = control_boosting)
boosting_train
```

- Random forests for 28 days (refine)
```{r}
control_rf <- trainControl(method = "repeatedcv",number = 5,repeats = 3,search = "grid")
set.seed(3)
tunegrid_rf <- expand.grid(mtry = c(2:8))
rf_train <- train(X28d.strength..psi. ~ FIneness..m2.kg. + SO3.... + CaO.... + Al2O3.... + C3A_pct + C2S_pct + Na2O_pct + K2O_pct,data = result.data.2,methods = "rf",metric = "RMSE",tuneGrid = tunegrid_rf, trControl = control_rf)
print(rf_train)
```

- Extremely random forests for 28 days (refine)
```{r}
et_grid <- expand.grid(mtry = 2:8,numRandomCuts = 1:5)
set.seed(3)
control_et = trainControl(method = "cv", number = 5)
et_train <- train(X28d.strength..psi. ~ FIneness..m2.kg. + SO3.... + CaO.... + Al2O3.... + C3A_pct + C2S_pct + Na2O_pct + K2O_pct,data = result.data.2,method = "extraTrees",numThreads = 4, tuneGrid = et_grid,trControl = control_et)
et_train
```

- Cross validation
```{r}
cv_function <- function(x){
  # Empty sets
  MSE_linear_3 <- c()
  MSE_linear_7 <- c()
  MSE_linear_28 <- c()
  MSE_KNN_3 <- c()
  MSE_KNN_7 <- c()
  MSE_KNN_28 <- c()
  MSE_bagged_3 <- c()
  MSE_bagged_7 <- c()
  MSE_bagged_28 <- c()
  MSE_Xgboost_3 <- c()
  MSE_Xgboost_7 <- c()
  MSE_Xgboost_28 <- c()
  MSE_RF_3 <- c()
  MSE_RF_7 <- c()
  MSE_RF_28 <- c()
  MSE_ET_3 <- c()
  MSE_ET_7 <- c()
  MSE_ET_28 <- c()
  R2_linear_3 <- c()
  R2_linear_7 <- c()
  R2_linear_28 <- c()
  R2_KNN_3 <- c()
  R2_KNN_7 <- c()
  R2_KNN_28 <- c()
  R2_bagged_3 <- c()
  R2_bagged_7 <- c()
  R2_bagged_28 <- c()
  R2_Xgboost_3 <- c()
  R2_Xgboost_7 <- c()
  R2_Xgboost_28 <- c()
  R2_RF_3 <- c()
  R2_RF_7 <- c()
  R2_RF_28 <- c()
  R2_ET_3 <- c()
  R2_ET_7 <- c()
  R2_ET_28 <- c()
  
  # for loop
  for(i in 1:50){
  set.seed(10*i + (i^2 + 1))
  index <- sample(1:2194,1756); train <- x[index,]; test<- x[-index,]
  test_y_3 <- test$X3d.strength..psi.; test_y_7 <- test$X7d.strength..psi.; test_y_28 <- test$X28d.strength..psi.
  # linear model
  lmmodel_3 <- lm(X3d.strength..psi.^1.29 ~ FIneness..m2.kg. + SO3.... + CaO.... + Al2O3.... + SiO2.... + K2O_pct + Fe2O3...., data = train)
  yhat3 <- (predict(lmmodel_3,newdata = test))^(1/1.29)
  MSE_linear_3[i] <- mean((test[,17] - yhat3)^2)
  R2_linear_3[i] <- 1 - sum((yhat3 - test_y_3)^2) / sum((test_y_3 - mean(test_y_3))^2)
  
  lmmodel_7 <- lm(X7d.strength..psi.^1.61 ~ FIneness..m2.kg. + SO3.... + CaO.... + Al2O3.... + SiO2.... + Fe2O3.... + C3S_pct + C2S_pct, data = train)
  yhat7 <- (predict(lmmodel_7,newdata = test))^(1/1.61)
  MSE_linear_7[i] <- mean((test[,18] - yhat7)^2)
  R2_linear_7[i] <- 1 - sum((yhat7 - test_y_7)^2) / sum((test_y_7 - mean(test_y_7))^2)
  
  lmmodel_28 <- lm(X28d.strength..psi.^1.54 ~ FIneness..m2.kg. + SO3.... + CaO.... + Al2O3.... + C3A_pct + C2S_pct + Na2O_pct + K2O_pct, data = train)
  yhat28 <- (predict(lmmodel_28,newdata = test))^(1/1.54)
  MSE_linear_28[i] <- mean((test[,19] - yhat28)^2)
  R2_linear_28[i] <- 1 - sum((yhat28 - test_y_28)^2) / sum((test_y_28 - mean(test_y_28))^2)
  
  # KNN
  ctrl <- trainControl(method = "cv", number = 5)
  KNN_3 <- knnreg(x = train[,c(1:5,8,14)], y = train[,17], k = train(x = train[,c(1:5,8,14)], y = train[,17], method = "knn" , metric = "RMSE", trControl = ctrl)$bestTune$k)
  yhat3 <- predict(KNN_3, newdata = test[,c(1:5,8,14)])
  MSE_KNN_3[i] <- mean((yhat3 - test[,17])^2)
  R2_KNN_3[i] <- 1 - sum((yhat3 - test_y_3)^2) / sum((test_y_3 - mean(test_y_3))^2)
  
  KNN_7 <- knnreg(x = train[,c(1:8)], y = train[,18], k = train(x = train[,c(1:8)], y = train[,18], method = "knn" , metric = "RMSE", trControl = ctrl)$bestTune$k)
  yhat7 <- predict(KNN_7, newdata = test[,1:8])
  MSE_KNN_7[i] <- mean((yhat7 - test[,18])^2)
  R2_KNN_7[i] <- 1 - sum((yhat7 - test_y_7)^2) / sum((test_y_7 - mean(test_y_7))^2)
  
  KNN_28 <- knnreg(x = train[,c(1:4,8,9,13,14)], y = train[,19], k = train(x = train[,c(1:4,8,9,13,14)], y = train[,19], method = "knn" , metric = "RMSE", trControl = ctrl)$bestTune$k)
  yhat28 <- predict(KNN_28, newdata = test[,c(1:4,8,9,13,14)])
  MSE_KNN_28[i] <- mean((yhat28 - test[,19])^2)
  R2_KNN_28[i] <- 1 - sum((yhat28 - test_y_28)^2) / sum((test_y_28 - mean(test_y_28))^2)
  
  # Bagged
  bagged_3 <- randomForest(X3d.strength..psi. ~ FIneness..m2.kg. + SO3.... + CaO.... + Al2O3.... + SiO2.... + K2O_pct + C2S_pct,mtry = 7,data = train,importance = T)
  yhat3 <- predict(bagged_3,newdata = test)
  MSE_bagged_3[i] <- mean((yhat3 - test[,17])^2)
  R2_bagged_3[i] <- 1 - sum((yhat3 - test_y_3)^2) / sum((test_y_3 - mean(test_y_3))^2)
  
  bagged_7 <- randomForest(X7d.strength..psi. ~ FIneness..m2.kg. + SO3.... + CaO.... + Al2O3.... + SiO2.... + Fe2O3.... + C3S_pct + C2S_pct,mtry = 8,data = train,importance = T)
  yhat7 <- predict(bagged_7,newdata = test)
  MSE_bagged_7[i] <- mean((yhat7 - test[,18])^2)
  R2_bagged_7[i] <- 1 - sum((yhat7 - test_y_7)^2) / sum((test_y_7 - mean(test_y_7))^2)
  
  bagged_28 <- randomForest(X28d.strength..psi. ~ FIneness..m2.kg. + SO3.... + CaO.... + Al2O3.... + C3A_pct + C2S_pct + Na2O_pct + K2O_pct,mtry = 8,data = train,importance = T)
  yhat28 <- predict(bagged_28,newdata = test)
  MSE_bagged_28[i] <- mean((yhat28 - test[,19])^2)
  R2_bagged_28[i] <- 1 - sum((yhat28 - test_y_28)^2) / sum((test_y_28 - mean(test_y_28))^2)
  
  # XgBoosting
  Xgboost_3 <-train(X3d.strength..psi. ~ FIneness..m2.kg. + SO3.... + CaO.... + Al2O3....
  + SiO2.... + K2O_pct + C2S_pct, data = train, method = "xgbTree",
  trControl = trainControl("cv", number = 5))
  yhat3 <- predict(Xgboost_3,newdata = test)
  MSE_Xgboost_3[i] <- mean((yhat3 - test[,17])^2)
  R2_Xgboost_3[i] <- 1 - sum((yhat3 - test_y_3)^2) / sum((test_y_3 - mean(test_y_3))^2)
  
  
  Xgboost_7 <-train(X7d.strength..psi. ~ FIneness..m2.kg. + SO3.... + CaO.... + Al2O3....   + SiO2.... + Fe2O3.... + C3S_pct + C2S_pct, data = train, method = "xgbTree",
  trControl = trainControl("cv", number = 5))
  yhat7 <- predict(Xgboost_7,newdata = test)
  MSE_Xgboost_7[i] <- mean((yhat7 - test[,18])^2)
  R2_Xgboost_7[i] <- 1 - sum((yhat7 - test_y_7)^2) / sum((test_y_7 - mean(test_y_7))^2)
  
  Xgboost_28 <-train(
  X28d.strength..psi. ~ FIneness..m2.kg. + SO3.... + CaO.... + Al2O3.... + C3A_pct + C2S_pct + Na2O_pct + K2O_pct, data = train, method = "xgbTree",
  trControl = trainControl("cv", number = 5)
  )
  yhat28 <- predict(Xgboost_28,newdata = test)
  MSE_Xgboost_28[i] <- mean((yhat28 - test[,19])^2)
  R2_Xgboost_28[i] <- 1 - sum((yhat28 - test_y_28)^2) / sum((test_y_28 - mean(test_y_28))^2)
  
  # Random forest
  control_rf <- trainControl(method = "repeatedcv",number = 5,repeats = 3,search = "grid")
  
  tunegrid_rf <- expand.grid(mtry = c(2:7))
  rf_3 <- train(X3d.strength..psi. ~ FIneness..m2.kg. + SO3.... + CaO.... + Al2O3.... + SiO2.... + K2O_pct + C2S_pct,data = train,methods = "rf",metric = "RMSE",tuneGrid = tunegrid_rf, trControl = control_rf)
  yhat3 <- predict(rf_3,newdata = test)
  MSE_RF_3[i] <- mean((yhat3 - test[,17])^2)
  R2_RF_3[i] <- 1 - sum((yhat3 - test_y_3)^2) / sum((test_y_3 - mean(test_y_3))^2)
  
  tunegrid_rf <- expand.grid(mtry = c(2:8))
  rf_7 <- train(X7d.strength..psi. ~ FIneness..m2.kg. + SO3.... + CaO.... + Al2O3.... + SiO2.... + Fe2O3.... + C3S_pct + C2S_pct,data = train,methods = "rf",metric = "RMSE",tuneGrid = tunegrid_rf, trControl = control_rf)
  yhat7 <- predict(rf_7,newdata = test)
  MSE_RF_7[i] <- mean((yhat7 - test[,18])^2)
  R2_RF_7[i] <- 1 - sum((yhat7 - test_y_7)^2) / sum((test_y_7 - mean(test_y_7))^2)
  
  tunegrid_rf <- expand.grid(mtry = c(2:8))
  rf_28 <- train(X28d.strength..psi. ~ FIneness..m2.kg. + SO3.... + CaO.... + Al2O3.... + C3A_pct + C2S_pct + Na2O_pct + K2O_pct,data = train,methods = "rf",metric = "RMSE",tuneGrid = tunegrid_rf, trControl = control_rf)
  yhat28 <- predict(rf_28,newdata = test)
  MSE_RF_28[i] <- mean((yhat28 - test[,19])^2)
  R2_RF_28[i] <- 1 - sum((yhat28 - test_y_28)^2) / sum((test_y_28 - mean(test_y_28))^2)
  
  # Extremely random forests
  control_et = trainControl(method = "cv", number = 5)
  
  et_grid <- expand.grid(mtry = 2:7,numRandomCuts = 1:5)
  et_3 <- train(X3d.strength..psi. ~ FIneness..m2.kg. + SO3.... + CaO.... + Al2O3.... + SiO2.... + K2O_pct + C2S_pct,data = train,method = "extraTrees",numThreads = 4, tuneGrid = et_grid,trControl = control_et)
  yhat3 <- predict(et_3,newdata = test)
  MSE_ET_3[i] <- mean((yhat3 - test[,17])^2)
  R2_ET_3[i] <- 1 - sum((yhat3 - test_y_3)^2) / sum((test_y_3 - mean(test_y_3))^2)
  
  et_grid <- expand.grid(mtry = 2:8,numRandomCuts = 1:5)
  et_7 <- train(X7d.strength..psi. ~ FIneness..m2.kg. + SO3.... + CaO.... + Al2O3.... + SiO2.... + Fe2O3.... + C3S_pct + C2S_pct,data = train,method = "extraTrees",numThreads = 4, tuneGrid = et_grid,trControl = control_et)
  yhat7 <- predict(et_7,newdata = test)
  MSE_ET_7[i] <- mean((yhat7 - test[,18])^2)
  R2_ET_7[i] <- 1 - sum((yhat7 - test_y_7)^2) / sum((test_y_7 - mean(test_y_7))^2)
  
  et_grid <- expand.grid(mtry = 2:8,numRandomCuts = 1:5)
  et_28 <- train(X28d.strength..psi. ~ FIneness..m2.kg. + SO3.... + CaO.... + Al2O3.... + C3A_pct + C2S_pct + Na2O_pct + K2O_pct,data = train,method = "extraTrees",numThreads = 4, tuneGrid = et_grid,trControl = control_et)
  yhat28 <- predict(et_28,newdata = test)
  MSE_ET_28[i] <- mean((yhat28 - test[,19])^2)
  R2_ET_28[i] <- 1 - sum((yhat28 - test_y_28)^2) / sum((test_y_28 - mean(test_y_28))^2)
  
  }
  # mean of sets
  sumtable <<- data.frame("Linear_MSE" = 0.00689476*sqrt(c(mean(MSE_linear_3),mean(MSE_linear_7),mean(MSE_linear_28))),"Linear_R2" = c(mean(R2_linear_3),mean(R2_linear_7),mean(R2_linear_28)),"KNN_MSE" = 0.00689476*sqrt(c(mean(MSE_KNN_3),mean(MSE_KNN_7),mean(MSE_KNN_28))),"KNN_R2" = c(mean(R2_KNN_3),mean(R2_KNN_7),mean(R2_KNN_28)), "Bagged_MSE" = 0.00689476*sqrt(c(mean(MSE_bagged_3),mean(MSE_bagged_7),mean(MSE_bagged_28))), "Bagged _R2" = c(mean(R2_bagged_3),mean(R2_bagged_7),mean(R2_bagged_28)), "Xgboost_MSE" = 0.00689476*sqrt(c(mean(MSE_Xgboost_3),mean(MSE_Xgboost_7),mean(MSE_Xgboost_28))),"Xgboost_R2" = c(mean(R2_Xgboost_3),mean(R2_Xgboost_7),mean(R2_Xgboost_28)),"RF_MSE" = 0.00689476*sqrt(c(mean(MSE_RF_3),mean(MSE_RF_7),mean(MSE_RF_28))),"RF_R2" = c(mean(R2_RF_3),mean(R2_RF_7),mean(R2_RF_28)) ,"ET_MSE" = 0.00689476*sqrt(c(mean(MSE_ET_3),mean(MSE_ET_7),mean(MSE_ET_28))),"ET_R2" = c(mean(R2_ET_3),mean(R2_ET_7),mean(R2_ET_28)))
  
print(sumtable)
} 


ptm <- proc.time()
cv_function(result.data.3)
proc.time() - ptm

sumtable$Linear_full_MSE <- total$Linear_full_MSE
sumtable$Linear_full_R2 <- total$Linear_full_R2
sumtable
```

- Gaussian Process Regression
```{r}
ggpred_3_R <- c()
ggpred_7_R <- c()
ggpred_28_R <- c()
for (i in 1:10) {
set.seed(i*10+(i^2+41))
index <- sample(1:2194,1756); train <- result.data.3[index,]; test<- result.data.3[-index,]
test_y_3 <- test$X3d.strength..psi.; test_y_7 <- test$X7d.strength..psi.; test_y_28 <- test$X28d.strength..psi.

gpr_grid <- expand.grid(sigma = c(0.001,0.0015,0.012,0.015,0.01,0.05,0.1,0.5,0.9,1,2))
ctrl <- trainControl(method = "cv",number = 5)

gpr_3 <- train(X3d.strength..psi. ~ FIneness..m2.kg. + SO3.... + CaO.... + Al2O3.... + SiO2.... + Fe2O3....+C3S_pct+C2S_pct+C3A_pct+C4AF_pct+FreeCaO_pct+MgO_pct+Na2O_pct+K2O_pct+LOI_pct, data = train, method = "gaussprRadial",tuneGrid = gpr_grid,trControl = ctrl)
ggpred_3 <- predict(gpr_3,newdata = test)
ggpred_3_R[i] <- 1 - sum((ggpred_3 - test$X3d.strength..psi.)^2) / sum((test$X3d.strength..psi. - mean(test$X3d.strength..psi.))^2)

gpr_7 <- train(X7d.strength..psi. ~ FIneness..m2.kg. + SO3.... + CaO.... + Al2O3.... + SiO2.... + Fe2O3....+C3S_pct+C2S_pct+C3A_pct+C4AF_pct+FreeCaO_pct+MgO_pct+Na2O_pct+K2O_pct+LOI_pct, data = train, method = "gaussprRadial",tuneGrid = gpr_grid,trControl = ctrl)
ggpred_7 <- predict(gpr_7,newdata = test)
ggpred_7_R[i] <- 1 - sum((ggpred_7 - test$X7d.strength..psi.)^2) / sum((test$X7d.strength..psi. - mean(test$X7d.strength..psi.))^2)

gpr_28 <- train(X28d.strength..psi. ~ FIneness..m2.kg. + SO3.... + CaO.... + Al2O3.... + SiO2.... + Fe2O3....+C3S_pct+C2S_pct+C3A_pct+C4AF_pct+FreeCaO_pct+MgO_pct+Na2O_pct+K2O_pct+LOI_pct, data = train, method = "gaussprRadial",tuneGrid = gpr_grid,trControl = ctrl)
ggpred_28 <- predict(gpr_28,newdata = test)
ggpred_28_R[i] <- 1 - sum((ggpred_28 - test$X28d.strength..psi.)^2) / sum((test$X28d.strength..psi. - mean(test$X28d.strength..psi.))^2)

}

# ggg <- gausspr(X3d.strength..psi. ~ FIneness..m2.kg. + SO3.... + CaO.... + Al2O3.... + SiO2.... + Fe2O3....+C3S_pct+C2S_pct+C3A_pct+C4AF_pct+FreeCaO_pct+MgO_pct+Na2O_pct+K2O_pct+LOI_pct, data = train,type = "regression",kernel = "rbfdot",cross = 5,sigma = 1)

mean(ggpred_3_R)
mean(ggpred_7_R)
mean(ggpred_28_R)

```

- ANN and GPR
```{r}
R2_ANN_3 <- c()
ANN_3_rmse <-c()
R2_ANN_7 <- c()
ANN_7_rmse <- c()
R2_ANN_28 <- c()
ANN_28_rmse <- c()
ggpred_3_R <- c()
ggpred_7_R <- c()
ggpred_28_R <- c()

for(i in 1:30){
set.seed(10*i + (i^2 + 1))
aaaaa<-as.data.frame(scale(result.data.3))
index <- sample(1:2194,1756); train <- aaaaa[index,]; test<- aaaaa[-index,]
test_y_3 <- test$X3d.strength..psi.; test_y_7 <- test$X7d.strength..psi.; test_y_28 <- test$X28d.strength..psi.
my.grid <- expand.grid(.decay = c(0.5,0.1,0.01,0.001), .size = c(9,10,11,12,13,14))
gpr_grid <- expand.grid(sigma = c(0.001,0.0015,0.012,0.015,0.01,0.05,0.1,0.5,0.9,1,2))
ctrl <- trainControl(method = "cv",number = 5)

## ANN 
ANN_3 <- train(X3d.strength..psi. ~ FIneness..m2.kg. + SO3.... + CaO.... + Al2O3.... + SiO2.... + Fe2O3....+C3S_pct+C2S_pct+C3A_pct+C4AF_pct+FreeCaO_pct+MgO_pct+Na2O_pct+K2O_pct+LOI_pct, data = train,method = "nnet", maxit = 10000, tuneGrid = my.grid, trace = F, linout = 1,trControl = ctrl)  
ANN_3_pred <- predict(ANN_3, newdata = test)
ANN_3_rmse[i] <- sqrt(mean((ANN_3_pred - test$X3d.strength..psi.)^2)) 
R2_ANN_3[i] <- 1 - sum((ANN_3_pred - test$X3d.strength..psi.)^2) / sum((test$X3d.strength..psi. - mean(test$X3d.strength..psi.))^2)

ANN_7 <- train(X7d.strength..psi. ~ FIneness..m2.kg. + SO3.... + CaO.... + Al2O3.... + SiO2.... + Fe2O3....+C3S_pct+C2S_pct+C3A_pct+C4AF_pct+FreeCaO_pct+MgO_pct+Na2O_pct+K2O_pct+LOI_pct, data = train,method = "nnet", maxit = 10000, tuneGrid = my.grid, trace = F, linout = 1,trControl = ctrl)  
ANN_7_pred <- predict(ANN_7, newdata = test)
ANN_7_rmse[i] <- sqrt(mean((ANN_7_pred - test$X7d.strength..psi.)^2)) 
R2_ANN_7[i] <- 1 - sum((ANN_7_pred - test$X7d.strength..psi.)^2) / sum((test$X7d.strength..psi. - mean(test$X7d.strength..psi.))^2)

ANN_28 <- train(X28d.strength..psi. ~ FIneness..m2.kg. + SO3.... + CaO.... + Al2O3.... + SiO2.... + Fe2O3....+C3S_pct+C2S_pct+C3A_pct+C4AF_pct+FreeCaO_pct+MgO_pct+Na2O_pct+K2O_pct+LOI_pct, data = train,method = "nnet", maxit = 10000, tuneGrid = my.grid, trace = F, linout = 1,trControl = ctrl)  
ANN_28_pred <- predict(ANN_28, newdata = test)
ANN_28_rmse[i] <- sqrt(mean((ANN_28_pred - test$X28d.strength..psi.)^2)) 
R2_ANN_28[i] <- 1 - sum((ANN_28_pred - test$X28d.strength..psi.)^2) / sum((test$X28d.strength..psi. - mean(test$X28d.strength..psi.))^2)

## GPR
gpr_3 <- train(X3d.strength..psi. ~ FIneness..m2.kg. + SO3.... + CaO.... + Al2O3.... + SiO2.... + Fe2O3....+C3S_pct+C2S_pct+C3A_pct+C4AF_pct+FreeCaO_pct+MgO_pct+Na2O_pct+K2O_pct+LOI_pct, data = train, method = "gaussprRadial",tuneGrid = gpr_grid,trControl = ctrl)
ggpred_3 <- predict(gpr_3,newdata = test)
ggpred_3_R[i] <- 1 - sum((ggpred_3 - test$X3d.strength..psi.)^2) / sum((test$X3d.strength..psi. - mean(test$X3d.strength..psi.))^2)

gpr_7 <- train(X7d.strength..psi. ~ FIneness..m2.kg. + SO3.... + CaO.... + Al2O3.... + SiO2.... + Fe2O3....+C3S_pct+C2S_pct+C3A_pct+C4AF_pct+FreeCaO_pct+MgO_pct+Na2O_pct+K2O_pct+LOI_pct, data = train, method = "gaussprRadial",tuneGrid = gpr_grid,trControl = ctrl)
ggpred_7 <- predict(gpr_7,newdata = test)
ggpred_7_R[i] <- 1 - sum((ggpred_7 - test$X7d.strength..psi.)^2) / sum((test$X7d.strength..psi. - mean(test$X7d.strength..psi.))^2)

gpr_28 <- train(X28d.strength..psi. ~ FIneness..m2.kg. + SO3.... + CaO.... + Al2O3.... + SiO2.... + Fe2O3....+C3S_pct+C2S_pct+C3A_pct+C4AF_pct+FreeCaO_pct+MgO_pct+Na2O_pct+K2O_pct+LOI_pct, data = train, method = "gaussprRadial",tuneGrid = gpr_grid,trControl = ctrl)
ggpred_28 <- predict(gpr_28,newdata = test)
ggpred_28_R[i] <- 1 - sum((ggpred_28 - test$X28d.strength..psi.)^2) / sum((test$X28d.strength..psi. - mean(test$X28d.strength..psi.))^2)

  
}
mean(R2_ANN_3) 
mean(R2_ANN_7) 
mean(R2_ANN_28) 
mean(ggpred_3_R)
mean(ggpred_7_R)
mean(ggpred_28_R)


# rctrlR <- trainControl(method = "cv", number = 3, returnResamp = "all", search = "random")
# test_reg_cv_model <- train(X3d.strength..psi. ~ FIneness..m2.kg. + SO3.... + CaO.... + Al2O3.... + SiO2.... + Fe2O3....+C3S_pct+C2S_pct+C3A_pct+C4AF_pct+FreeCaO_pct+MgO_pct+Na2O_pct+K2O_pct+LOI_pct, data = train, method = "neuralnet", trControl = rctrlR,
#                            tuneGrid = data.frame(layer1 = 2:9, layer2 = 2:3, layer3 = 1),
#                            rep = 2,
#                            threshold = 0.1,        
#                            stepmax = 1e+05,
#                            preProc = c("center", "scale"))
```

- Time series analysis
```{r}
summary(p7 <- powerTransform(X7d.strength..psi. ~ X3d.strength..psi. + FIneness..m2.kg. + SO3.... + CaO.... + Al2O3.... + SiO2.... + Fe2O3.... + C3A_pct + C2S_pct, data = result.data.3))
TA_lm_7days <- lm(X7d.strength..psi.^1.29 ~ X3d.strength..psi. + FIneness..m2.kg. + SO3.... + CaO.... + Al2O3.... + SiO2.... + Fe2O3.... + C3A_pct + C2S_pct, data = result.data.3)
summary(TA_lm_7days)
plot(TA_lm_7days)
lm.beta(TA_lm_7days)

summary(p28 <- powerTransform(X28d.strength..psi. ~ X7d.strength..psi. + FIneness..m2.kg. + SO3.... + SiO2.... + C3S_pct + C3A_pct + C2S_pct + Na2O_pct + K2O_pct, data = result.data.3))
TA_lm_28days <- lm(X28d.strength..psi. ~ X7d.strength..psi. + FIneness..m2.kg. + SO3.... + SiO2.... + C3S_pct + C3A_pct + C2S_pct + Na2O_pct + K2O_pct, data = result.data.3)
summary(TA_lm_28days)
plot(TA_lm_28days)
lm.beta(TA_lm_28days)
```

- CV function for time series
```{r}
cv_function_time_series <- function(x){
  # Empty sets
  MSE_linear_7 <- c()
  MSE_linear_28 <- c()
  MSE_KNN_7 <- c()
  MSE_KNN_28 <- c()
  MSE_bagged_7 <- c()
  MSE_bagged_28 <- c()
  MSE_Xgboost_3 <- c()
  MSE_Xgboost_7 <- c()
  MSE_Xgboost_28 <- c()
  MSE_RF_7 <- c()
  MSE_RF_28 <- c()
  MSE_ET_7 <- c()
  MSE_ET_28 <- c()
  R2_linear_7 <- c()
  R2_linear_28 <- c()
  R2_KNN_7 <- c()
  R2_KNN_28 <- c()
  R2_bagged_7 <- c()
  R2_bagged_28 <- c()
  R2_Xgboost_7 <- c()
  R2_Xgboost_28 <- c()
  R2_RF_7 <- c()
  R2_RF_28 <- c()
  R2_ET_7 <- c()
  R2_ET_28 <- c()
  
  # for loop
  for(i in 1:30){
  set.seed(10*i + (i^2 + 1))
  index <- sample(1:2194,1756); train <- x[index,]; test<- x[-index,]
  test_y_3 <- test$X3d.strength..psi.; test_y_7 <- test$X7d.strength..psi.; test_y_28 <- test$X28d.strength..psi.
  # linear model
  
  lmmodel_7 <- lm(X7d.strength..psi.^1.29 ~ X3d.strength..psi. + FIneness..m2.kg. + SO3.... + CaO.... + Al2O3.... + SiO2.... + Fe2O3.... + C3A_pct + C2S_pct, data = train)
  yhat7 <- (predict(lmmodel_7,newdata = test))^(1/1.61)
  MSE_linear_7[i] <- mean((test[,18] - yhat7)^2)
  R2_linear_7[i] <- 1 - sum((yhat7 - test_y_7)^2) / sum((test_y_7 - mean(test_y_7))^2)
  
  lmmodel_28 <- lm(X28d.strength..psi. ~ X7d.strength..psi. + FIneness..m2.kg. + SO3.... + SiO2.... + C3S_pct + C3A_pct + C2S_pct + Na2O_pct + K2O_pct, data = train)
  yhat28 <- (predict(lmmodel_28,newdata = test))^(1/1.54)
  MSE_linear_28[i] <- mean((test[,19] - yhat28)^2)
  R2_linear_28[i] <- 1 - sum((yhat28 - test_y_28)^2) / sum((test_y_28 - mean(test_y_28))^2)
  
  # KNN
  
  KNN_7 <- knnreg(x = train[,c(1:15,17)], y = train[,18], k = train(x = train[,c(1:8)], y = train[,18], method = "knn" , metric = "RMSE", trControl = ctrl)$bestTune$k)
  yhat7 <- predict(KNN_7, newdata = test[,1:15,17])
  MSE_KNN_7[i] <- mean((yhat7 - test[,18])^2)
  R2_KNN_7[i] <- 1 - sum((yhat7 - test_y_7)^2) / sum((test_y_7 - mean(test_y_7))^2)
  
  KNN_28 <- knnreg(x = train[,c(1:5,18)], y = train[,19], k = train(x = train[,c(1:15,18)], y = train[,19], method = "knn" , metric = "RMSE", trControl = ctrl)$bestTune$k)
  yhat28 <- predict(KNN_28, newdata = test[,c(1:15,18)])
  MSE_KNN_28[i] <- mean((yhat28 - test[,19])^2)
  R2_KNN_28[i] <- 1 - sum((yhat28 - test_y_28)^2) / sum((test_y_28 - mean(test_y_28))^2)
  
  # Bagged
  
  bagged_7 <- randomForest(X7d.strength..psi. ~ X3d.strength..psi. + FIneness..m2.kg. + SO3.... + CaO.... + Al2O3.... + SiO2.... + Fe2O3....+C3S_pct+C2S_pct+C3A_pct+C4AF_pct+FreeCaO_pct+MgO_pct+Na2O_pct+K2O_pct+LOI_pct,mtry = 16,data = train,importance = T)
  yhat7 <- predict(bagged_7,newdata = test)
  MSE_bagged_7[i] <- mean((yhat7 - test[,18])^2)
  R2_bagged_7[i] <- 1 - sum((yhat7 - test_y_7)^2) / sum((test_y_7 - mean(test_y_7))^2)
  
  bagged_28 <- randomForest(X28d.strength..psi. ~ X7d.strength..psi. + FIneness..m2.kg. + SO3.... + CaO.... + Al2O3.... + SiO2.... + Fe2O3....+C3S_pct+C2S_pct+C3A_pct+C4AF_pct+FreeCaO_pct+MgO_pct+Na2O_pct+K2O_pct+LOI_pct,mtry = 16,data = train,importance = T)
  yhat28 <- predict(bagged_28,newdata = test)
  MSE_bagged_28[i] <- mean((yhat28 - test[,19])^2)
  R2_bagged_28[i] <- 1 - sum((yhat28 - test_y_28)^2) / sum((test_y_28 - mean(test_y_28))^2)
  
  # XgBoosting
  
  Xgboost_7 <-train(X7d.strength..psi. ~ X3d.strength..psi. + FIneness..m2.kg. + SO3.... + CaO.... + Al2O3.... + SiO2.... + Fe2O3....+C3S_pct+C2S_pct+C3A_pct+C4AF_pct+FreeCaO_pct+MgO_pct+Na2O_pct+K2O_pct+LOI_pct, data = train, method = "xgbTree",
  trControl = trainControl("cv", number = 5))
  yhat7 <- predict(Xgboost_7,newdata = test)
  MSE_Xgboost_7[i] <- mean((yhat7 - test[,18])^2)
  R2_Xgboost_7[i] <- 1 - sum((yhat7 - test_y_7)^2) / sum((test_y_7 - mean(test_y_7))^2)
  
  Xgboost_28 <-train(
  X28d.strength..psi. ~ X7d.strength..psi. + FIneness..m2.kg. + SO3.... + CaO.... + Al2O3.... + SiO2.... + Fe2O3....+C3S_pct+C2S_pct+C3A_pct+C4AF_pct+FreeCaO_pct+MgO_pct+Na2O_pct+K2O_pct+LOI_pct, data = train, method = "xgbTree",
  trControl = trainControl("cv", number = 5)
  )
  yhat28 <- predict(Xgboost_28,newdata = test)
  MSE_Xgboost_28[i] <- mean((yhat28 - test[,19])^2)
  R2_Xgboost_28[i] <- 1 - sum((yhat28 - test_y_28)^2) / sum((test_y_28 - mean(test_y_28))^2)
  
  # Random forest
  control_rf <- trainControl(method = "repeatedcv",number = 5,repeats = 3,search = "grid")
  
  tunegrid_rf <- expand.grid(mtry = c(2:8))
  rf_7 <- train(X7d.strength..psi. ~ X3d.strength..psi. + FIneness..m2.kg. + SO3.... + CaO.... + Al2O3.... + SiO2.... + Fe2O3....+C3S_pct+C2S_pct+C3A_pct+C4AF_pct+FreeCaO_pct+MgO_pct+Na2O_pct+K2O_pct+LOI_pct,data = train,methods = "rf",metric = "RMSE",tuneGrid = tunegrid_rf, trControl = control_rf)
  yhat7 <- predict(rf_7,newdata = test)
  MSE_RF_7[i] <- mean((yhat7 - test[,18])^2)
  R2_RF_7[i] <- 1 - sum((yhat7 - test_y_7)^2) / sum((test_y_7 - mean(test_y_7))^2)
  
  tunegrid_rf <- expand.grid(mtry = c(2:8))
  rf_28 <- train(X28d.strength..psi. ~ X7d.strength..psi. + FIneness..m2.kg. + SO3.... + CaO.... + Al2O3.... + SiO2.... + Fe2O3....+C3S_pct+C2S_pct+C3A_pct+C4AF_pct+FreeCaO_pct+MgO_pct+Na2O_pct+K2O_pct+LOI_pct,data = train,methods = "rf",metric = "RMSE",tuneGrid = tunegrid_rf, trControl = control_rf)
  yhat28 <- predict(rf_28,newdata = test)
  MSE_RF_28[i] <- mean((yhat28 - test[,19])^2)
  R2_RF_28[i] <- 1 - sum((yhat28 - test_y_28)^2) / sum((test_y_28 - mean(test_y_28))^2)
  
  # Extremely random forests
  control_et = trainControl(method = "cv", number = 5)
  
  et_grid <- expand.grid(mtry = 2:15,numRandomCuts = 1:5)
  et_7 <- train(X7d.strength..psi. ~ X3d.strength..psi. + FIneness..m2.kg. + SO3.... + CaO.... + Al2O3.... + SiO2.... + Fe2O3....+C3S_pct+C2S_pct+C3A_pct+C4AF_pct+FreeCaO_pct+MgO_pct+Na2O_pct+K2O_pct+LOI_pct,data = train,method = "extraTrees",numThreads = 4, tuneGrid = et_grid,trControl = control_et)
  yhat7 <- predict(et_7,newdata = test)
  MSE_ET_7[i] <- mean((yhat7 - test[,18])^2)
  R2_ET_7[i] <- 1 - sum((yhat7 - test_y_7)^2) / sum((test_y_7 - mean(test_y_7))^2)
  
  et_grid <- expand.grid(mtry = 2:15,numRandomCuts = 1:5)
  et_28 <- train(X28d.strength..psi. ~ X7d.strength..psi. + FIneness..m2.kg. + SO3.... + CaO.... + Al2O3.... + SiO2.... + Fe2O3....+C3S_pct+C2S_pct+C3A_pct+C4AF_pct+FreeCaO_pct+MgO_pct+Na2O_pct+K2O_pct+LOI_pct,data = train,method = "extraTrees",numThreads = 4, tuneGrid = et_grid,trControl = control_et)
  yhat28 <- predict(et_28,newdata = test)
  MSE_ET_28[i] <- mean((yhat28 - test[,19])^2)
  R2_ET_28[i] <- 1 - sum((yhat28 - test_y_28)^2) / sum((test_y_28 - mean(test_y_28))^2)
  
  }
  # mean of sets
  sumtable_Time_series <<- data.frame("Linear_MSE" = 0.00689476*sqrt(c(mean(MSE_linear_7),mean(MSE_linear_28))),"Linear_R2" = c(mean(R2_linear_7),mean(R2_linear_28)),"KNN_MSE" = 0.00689476*sqrt(c(mean(MSE_KNN_7),mean(MSE_KNN_28))),"KNN_R2" = c(mean(R2_KNN_7),mean(R2_KNN_28)), "Bagged_MSE" = 0.00689476*sqrt(c(mean(MSE_bagged_7),mean(MSE_bagged_28))), "Bagged _R2" = c(mean(R2_bagged_7),mean(R2_bagged_28)), "Xgboost_MSE" = 0.00689476*sqrt(c(mean(MSE_Xgboost_7),mean(MSE_Xgboost_28))),"Xgboost_R2" = c(mean(R2_Xgboost_7),mean(R2_Xgboost_28)),"RF_MSE" = 0.00689476*sqrt(c(mean(MSE_RF_7),mean(MSE_RF_28))),"RF_R2" = c(mean(R2_RF_7),mean(R2_RF_28)) ,"ET_MSE" = 0.00689476*sqrt(c(mean(MSE_ET_7),mean(MSE_ET_28))),"ET_R2" = c(mean(R2_ET_7),mean(R2_ET_28)))
  
print(sumtable_Time_series)
} 


ptm <- proc.time()
cv_function_time_series(result.data.3)
proc.time() - ptm
```

- ET
```{r}
cv_function_time_series_et <- function(x){
  # Empty sets
  # MSE_linear_7 <- c()
  # MSE_linear_28 <- c()
  # MSE_KNN_7 <- c()
  # MSE_KNN_28 <- c()
  # MSE_bagged_7 <- c()
  # MSE_bagged_28 <- c()
  # MSE_Xgboost_3 <- c()
  # MSE_Xgboost_7 <- c()
  # MSE_Xgboost_28 <- c()
  # MSE_RF_7 <- c()
  # MSE_RF_28 <- c()
  MSE_ET_7 <- c()
  MSE_ET_28 <- c()
  # R2_linear_7 <- c()
  # R2_linear_28 <- c()
  # R2_KNN_7 <- c()
  # R2_KNN_28 <- c()
  # R2_bagged_7 <- c()
  # R2_bagged_28 <- c()
  # R2_Xgboost_7 <- c()
  # R2_Xgboost_28 <- c()
  # R2_RF_7 <- c()
  # R2_RF_28 <- c()
  R2_ET_7 <- c()
  R2_ET_28 <- c()
  
  # for loop
  for(i in 1:30){
  set.seed(10*i + (i^2 + 1))
  index <- sample(1:2194,1756); train <- x[index,]; test<- x[-index,]
  test_y_3 <- test$X3d.strength..psi.; test_y_7 <- test$X7d.strength..psi.; test_y_28 <- test$X28d.strength..psi.
  
  # Extremely random forests
  control_et = trainControl(method = "cv", number = 5)
  
  et_grid <- expand.grid(mtry = 2:16,numRandomCuts = 1:5)
  et_7 <- train(X7d.strength..psi. ~ X3d.strength..psi. + FIneness..m2.kg. + SO3.... + CaO.... + Al2O3.... + SiO2.... + Fe2O3....+C3S_pct+C2S_pct+C3A_pct+C4AF_pct+FreeCaO_pct+MgO_pct+Na2O_pct+K2O_pct+LOI_pct,data = train,method = "extraTrees",numThreads = 4, tuneGrid = et_grid,trControl = control_et)
  yhat7 <- predict(et_7,newdata = test)
  MSE_ET_7[i] <- mean((yhat7 - test[,18])^2)
  R2_ET_7[i] <- 1 - sum((yhat7 - test_y_7)^2) / sum((test_y_7 - mean(test_y_7))^2)
  
  et_grid <- expand.grid(mtry = 2:16,numRandomCuts = 1:5)
  et_28 <- train(X28d.strength..psi. ~ X7d.strength..psi. + FIneness..m2.kg. + SO3.... + CaO.... + Al2O3.... + SiO2.... + Fe2O3....+C3S_pct+C2S_pct+C3A_pct+C4AF_pct+FreeCaO_pct+MgO_pct+Na2O_pct+K2O_pct+LOI_pct,data = train,method = "extraTrees",numThreads = 4, tuneGrid = et_grid,trControl = control_et)
  yhat28 <- predict(et_28,newdata = test)
  MSE_ET_28[i] <- mean((yhat28 - test[,19])^2)
  R2_ET_28[i] <- 1 - sum((yhat28 - test_y_28)^2) / sum((test_y_28 - mean(test_y_28))^2)
  
  }
  # mean of sets
  sumtable_Time_series <<- data.frame("ET_MSE" = 0.00689476*sqrt(c(mean(MSE_ET_7),mean(MSE_ET_28))),"ET_R2" = c(mean(R2_ET_7),mean(R2_ET_28)))
  
print(sumtable_Time_series)
} 

ptm <- proc.time()
cv_function_time_series_et(result.data.3)
proc.time() - ptm
```

